Comparative vaccine effectiveness of ChAdOx1 versus BNT162b2 in Health and Social Care workers in England

### 2021-09-01 analysis/report/draft-manuscript.Rmd
update title

---
title: "Comparative vaccine effectiveness (ChAdOx1 versus BNT162b2) in Health and Social Care workers"
output:
  html_document: 
    keep_md: yes
  word_document: default
  bookdown::html_document2:
    number_sections: false
    toc: false
bibliography: references.bib
csl: nature.csl # from https://raw.githubusercontent.com/citation-style-language/styles/master/nature.csl
link-citations: yes
zotero: true
---

>>>>

---
title: "Comparative vaccine effectiveness of ChAdOx1 versus BNT162b2 in Health and Social Care workers in England"
output:
  html_document: 
    keep_md: yes
  word_document: default
  bookdown::html_document2:
    number_sections: false
    toc: false
bibliography: references.bib
csl: nature.csl # from https://raw.githubusercontent.com/citation-style-language/styles/master/nature.csl
link-citations: yes
zotero: true
---
